---
title: "DDP Final Pitch"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objective

The objective of this presentation is to describe an app built in Shiny that allows you to explore the MTCars dataset.  

## The App & Instructions

The application is available at this link: https://nedcartmell.shinyapps.io/mtcars/

It plots MPG for the MTCars dataset against horsepower, while also coloring the number of cylinders in the engine.  Users can adjust the slide bars for Horsepower and Engine Displacment in order to restrict the portion of the dataset that they wish to see.  

It is very simple to use - simply adjust the slider bars to represent 

## Data

The MTCars dataset is a data frame consisting of 32 observations of 11 variables relating to performance and other characteristics of various models of cars.  You can read more about the dataset here: https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html

## Here is an example of some R code

```{r cars, echo = TRUE}
summary(mtcars$mpg)
```

## Au Revoir!

```{r pressure}
plot(mpg ~ hp, data = mtcars)
```

